### 2020-10-09 input/background.tex
meow

\begin{figure*}
  \begin{center}
    \subfloat[Part A][\label{fig:addA}Both Process $a$ and
      Process $c$ initiate a partition.
      $w_{ab} = 1.5$; $w_{bc} = w_{cd} = w_{bd} = 1$.]{\input{input/figaddA.tex}}
    \hspace{5pt}
    \subfloat[Part B][\label{fig:addB}Messages transit through communication
      links and carry increasing weights.]{\input{input/figaddB.tex}}
    \hspace{5pt}
    \subfloat[Part C][\label{fig:addC}Process $b$ receives and forwards
      $Add_{c, 1}$ then discards $Add_{a, 1.5}$, for the latter distance
      is higher.]{\input{input/figaddC.tex}}
    \hspace{5pt}
    \subfloat[Part D][\label{fig:addD}Processes $b$, $c$, and $d$ discard
      incoming messages. The system converged to optimal partitions.]{
      \input{input/figaddD.tex}}
    \caption{\label{fig:add}Simple accumulation in messages makes the
      system converge to optimal partitions with contained
      broadcast.}
  \end{center}
\end{figure*}

@@

When $distance$ involves monotonically increasing scalars such as
latency or number of hops between sources and processes, the optimal
partitioning consists in processing the multiple destinations shortest
path~\REF at each process.  Algorithm~\ref{algo:add} shows the
instructions of such dynamic partitioning where the only operation
available to processes is the adding of a
partition. Figure~\ref{fig:add} illustrates its behavior on a system
comprising 4 processes $a$, $b$, $c$, and $d$. Two processes $a$ and
$c$ concurrently create a partition. They initialize their own state
with the lowest possible bound $0$ (see Line~\ref{line:lowestbound}),
and send a message to each of their neighbors by accumulating the
corresponding edge weight (see Line~\ref{line:accumulator}). In
Figure~\ref{fig:addC}, Process $b$ receives $Add_{c, 1}$. Since it
improves its own partition distance, it keeps it and forwards it to
its neighbors. Process $b$ discards $Add_{b, 1.5}$, for it does not
improve its partition distance. Processes $c$ and $d$ will never hear
of Process $a$'s partition. \TODO{At scale.} In Figure~\ref{fig:addD},
processes discard last transiting messages. The system converged to
the optimal partitioning.

Transitive relationships ensure that each process gets its closest
source while accumulators ensure that messages propagation
terminates. The system converges towards the optimal partitioning
despite processes not broadcasting all messages. Removals of
partitions are more challenging. \TODO{Figure.} \TODO{Also easy to
  solve when all processes receive all messages}. One could solve this
issue by removing partitions that were not advertised for a defined
time~\REF. However, relying on physical timeout could lead to either
premature removals of partitions when they are still operating; or
slow convergence where processes believe they belong to a partition
that was removed.

\begin{figure*}
  \begin{center}
    \subfloat[Part A][\label{fig:delA}Both Process $a$ and
      Process $c$ initiate then remove a partition.
      $w_{ab} = 1.5$; $w_{bc} = w_{cd} = w_{bd} = 1$.]{\input{input/figdelA.tex}}
    \hspace{5pt}
    \subfloat[Part B][\label{fig:delB}Process $b$ and Process $d$ receive and deliver
      messages based on their weights. $a$'s partition propagates to all processes.]
             {\input{input/figdelB.tex}}
    \hspace{5pt}
    \subfloat[Part C][\label{fig:delC}Process $c$'s partition reach $b$ and $d$.
      Its removal shortly follows. Process $b$ does not have any control
      information about partitions any more.]{\input{input/figdelC.tex}}
    \hspace{5pt}
    \subfloat[Part D][\label{fig:delD}Processes discard remaining messages.
      Process $b$ does not deliver $\delta_a$, for it already removed $a$ when
      Partition $c$ dominated it. Processes $c$ and $d$ remain in an incorrect
      partition.]{\input{input/figdelD.tex}}
  \end{center}
  \caption{\label{algo:add}Removing partition may lead to inconsistent states.}
\end{figure*}

>>>>

When $distance$ involves latency or number of hops between sources and
processes, the optimal partitioning consists in processing the
multiple destinations shortest path~\REF at each process.

\begin{figure*}
  \begin{center}
    \subfloat[Part A][\label{fig:addA}Both Process $a$ and
      Process $c$ initiate a partition.
      $w_{ab} = 1.5$; $w_{bc} = w_{cd} = w_{bd} = 1$.]{\input{input/figaddA.tex}}
    \hspace{5pt}
    \subfloat[Part B][\label{fig:addB}Messages transit through communication
      links and carry increasing weights.]{\input{input/figaddB.tex}}
    \hspace{5pt}
    \subfloat[Part C][\label{fig:addC}Process $b$ receives and forwards
      $\alpha_{c}^{1}$ then discards $\alpha_{a}^{1.5}$, for the latter distance
      is higher.]{\input{input/figaddC.tex}}
    \hspace{5pt}
    \subfloat[Part D][\label{fig:addD}Processes $b$, $c$, and $d$ discard
      incoming messages. The system converged to optimal partitions.]{
      \input{input/figaddD.tex}}
    \caption{\label{fig:add}Simple accumulation in messages makes the
      system converge to optimal partitions with contained
      broadcast.}
  \end{center}
\end{figure*}

@@

Algorithm~\ref{algo:add} shows the instructions of optimal
partitioning where the only operation available to processes is the
adding of partitions. Figure~\ref{fig:add} illustrates its behavior on
a system comprising 4 processes $a$, $b$, $c$, and $d$. Two processes
$a$ and $c$ concurrently create a partition. They initialize their own
state with the lowest possible bound $0$ (see
Line~\ref{line:lowestbound}), and send a message to each of their
neighbors by accumulating the corresponding edge weight (see
Line~\ref{line:accumulator}). In Figure~\ref{fig:addC}, Process $b$
receives $\alpha_{c}^{1}$. Since it improves its own partition
distance, it keeps it and forwards it to its neighbors. Process $b$
discards $\alpha_{b}^{1.5}$, for it does not improve its partition
distance. Processes $c$ and $d$ will never hear of Process $a$'s
partition. At scale, it saves bandwidth by limiting generated traffic
to subsets of processes. In Figure~\ref{fig:addD}, processes discard
last transiting messages. The system converged to the optimal
partitioning. Interestingly, while the receipt order of messages does
not impact on local control information, it impacts on control
information broadcast in the network.

Transitive relationships ensure that each process gets its closest
source while accumulation of weights ensures that messages propagation
terminates.  Removals of partitions are more
challenging. \TODO{Figure.} \TODO{Also easy to solve when all
  processes receive all messages}. One could solve this issue by
removing partitions that were not advertised for a defined
time~\REF. However, relying on physical timeout could lead to either
premature removals of partitions when they are still operating; or
slow convergence where processes believe they belong to a partition
that was removed.

\begin{figure*}
  \begin{center}
    \subfloat[Part A][\label{fig:delA}Both Process $a$ and
      Process $c$ initiate then remove a partition.
      $w_{ab} = 1.5$; $w_{bc} = w_{cd} = w_{bd} = 1$.]{\input{input/figdelA.tex}}
    \hspace{5pt}
    \subfloat[Part B][\label{fig:delB}Process $b$ and Process $d$ receive and deliver
      messages based on their weights. $a$'s partition propagates to all processes.]
             {\input{input/figdelB.tex}}
    \hspace{5pt}
    \subfloat[Part C][\label{fig:delC}Process $c$'s partition reach $b$ and $d$.
      Its removal shortly follows. Process $b$ does not have any control
      information about partitions any more.]{\input{input/figdelC.tex}}
    \hspace{5pt}
    \subfloat[Part D][\label{fig:delD}Processes discard remaining messages.
      Process $b$ does not deliver $\delta_a$, for it already removed $a$ when
      Partition $c$ dominated it. Processes $c$ and $d$ remain in an incorrect
      partition.]{\input{input/figdelD.tex}}
  \end{center}
  \caption{\label{algo:add}Removing partition may lead to inconsistent partitions.}
\end{figure*}
